A comparative risk assesment of U.S. regional active transport using the ITHIM model

### 2016-09-20 manuscript/manuscript.tex
Worked on Figures for Manuscript #1
Also updated the Make file in the top-level directory.  make all runs the whole thing now with dependencies in place.
Included @vargovargo edits in Abstract Summary

\section{Summary:}
\col[blue]{While increased active transportation, primarily cycling
  and walk, is often held up as a goal for improved public health —
  via reduced chronic disease, improved air quality, and reductions in
  greenhouse gas emissions --- obtaining estimates for the quantiative
  impacts of such shifts remains infrequent, in not altogether
  absent. Using U.S. metropolitan counties from the 10 regions defined
  by the Department of Health and Human Services (HHS1-10) we perform
  a comparative risk analysis between each regions and national
  averages as the baseline.  We investigated the reduced chronic
  disease burden of ($x$, $y$, $z$ outcomes) from increased physical
  activity from population shifts in the amount of biking and walking
  doen for transport.  Our methods employ the Integrated Transport and
  Health Impacts Model (ITHIM) informed by regional travel parameters
  using the National Household Transportation Survey, non-travel
  activity metircs from the American Time Use Survey, and baseline
  Disease burden from the Centers for Disease Control and Prevention's
  WONDER database.  Our findings show that the West coast and the
  Northeast of the U.S. have travel patterns that, if mirrored by the
  nation, would save the U.S. thousands to hundreds of thousands
  DALYs.}

>>>>

\section{Summary:}
\col[blue]{While increased active transportation, primarily cycling
  and walking, is often held up as a goal for improved public health —
  via reduced chronic disease, improved air quality, and reductions in
  greenhouse gas emissions --- obtaining estimates for the quantiative
  impacts of such shifts remains infrequent, if not altogether
  absent from related policy action. Using U.S. metropolitan counties from the 10 regions defined
  by the U.S. Department of Health and Human Services (HHS1-10) we perform
  a comparative risk analysis between each regions and national
  averages as the baseline.  We investigated the reduced chronic
  disease burden of ($x$, $y$, $z$ outcomes) from increased physical
  activity from population shifts in the amount of biking and walking
  doen for transport.  Our methods employ the Integrated Transport and
  Health Impacts Model (ITHIM) informed by regional travel parameters
  using the National Household Transportation Survey, non-travel
  activity metircs from the American Time Use Survey, and baseline
  Disease burden from the Centers for Disease Control and Prevention's
  WONDER database.  Our findings show that the West coast and the
  Northeast of the U.S. have travel patterns that, if mirrored by the
  nation, would save the U.S. thousands to hundreds of thousands
  DALYs.}
